Results

### 2025-08-27 notebooks/000_data.qmd
feat: new visualization with all enc in one panel

```{julia}
using Dates
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using SpacePhysicsMakie: tplot
import SpaceDataModel
using SpaceDataModel: setmeta, times
using TimeseriesUtilities
using Speasy
using GLMakie
using DataFrames, DimensionalData
```

@@

```{julia}
t0 = DateTime("2021-01-15T09:11")
t1 = DateTime("2021-01-15T09:14")
B_subset = tview(B, t0, t1)
V_subset = tview(V, t0, t1)
df_pvi = Discontinuity.ids_finder_PVI(B_subset, V_subset)
df_cvi = Discontinuity.ids_finder_CVI(B_subset, V_subset)
df_variance = Discontinuity.ids_finder(B_subset; tau=Second(30))

@@

# Plot 3 candidates from PVI method
for i in 1:min(3, nrow(df_pvi))
    plot_candidate(f[2, 1][i, 1], df_pvi[i, :], [PSP.B,])
end
for i in 1:min(3, nrow(df_cvi))
    plot_candidate(f[2, 2][i, 1], df_cvi[i, :], [PSP.B,])
end
for i in 1:min(3, nrow(df_variance))
    plot_candidate(f[2, 3][i, 1], df_variance[i, :], [PSP.B,])
end
f

```

>>>>

```{julia}
using Dates
using Speasy
using PSPAnisotropy
using PSP
using PSPAnisotropy: Wind, PSP, THEMIS
using SpacePhysicsMakie: tplot
import SpaceDataModel
using SpaceDataModel: setmeta, times, Product
using TimeseriesUtilities
using GLMakie
using DataFrames, DimensionalData
```

@@

```{julia}
tmin = DateTime("2021-01-15")
tmax = DateTime("2021-01-16")
B = DimArray(PSP.B(tmin, tmax))
V = DimArray(PSP.V(tmin, tmax))
```

```{julia}
t0 = DateTime("2021-01-15T09:11")
t1 = DateTime("2021-01-15T09:14")
B_subset = tview(B, t0, t1)
V_subset = tview(V, t0, t1)
df_pvi = Discontinuity.ids_finder_PVI(B_subset, V_subset)
df_cvi = Discontinuity.ids_finder_CVI(B_subset, V_subset)
df_variance = Discontinuity.ids_finder(B_subset; tau=Second(16))

@@

# Plot 3 candidates from PVI method
for i in 1:min(3, nrow(df_pvi))
    plot_candidate(f[2, 1][i, 1], df_pvi[i, :], [PSP.B,])
end
for i in 1:min(3, nrow(df_cvi))
    plot_candidate(f[2, 2][i, 1], df_cvi[i, :], [PSP.B,])
end
for i in 1:min(3, nrow(df_variance))
    plot_candidate(f[2, 3][i, 1], df_variance[i, :], [PSP.B,])
end
f
```

### 2025-08-27 notebooks/00_index.qmd
feat: new visualization with all enc in one panel

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using Discontinuity: compute_params!, compute_Alfvenicity_params!, filter_low_mva_quality
using SPEDAS
using DataFrames, DataFramesMeta
using GLMakie
using SPEDAS: setmeta, setmeta!
using Beforerr: _theme_legend, easy_save
using PartialFunctions

@@

@@

```{julia}
f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[5, :]
fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
@info "v_l_ratio" psp_event.V_l_ratio psp_event.V_l_ratio_max
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
f

```

@@

Alfvén ratio over time

@@

```{julia}
using AlgebraOfGraphics
using Discontinuity: compute_params!, compute_Alfvenicity_params!
using Beforerr
using Beforerr: add_labels!
using CairoMakie
using StatsBase
CairoMakie.activate!()

set_aog_theme!()
formats = (:pdf,)

@@

df, configs = workload()
𝐧 = :mva
𝒎 = var_mapping(; 𝐧)

compute_params!(df)

@@

subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df

@@

```{julia}
fname = "properties_hist-enc"

for enc in 7:9, 𝐧 in [:mva, :cross]
    view = true
    𝒎 = var_mapping(; 𝐧)
    datalimits_f = x -> quantile(x, [0.02, 0.98])
    # drop missing and NaN
    tdf = @chain df begin
        @subset(:enc .== enc, .!isnan.(:L_n_cross_norm); view)
        dropmissing
        subset_𝐧(𝐧)
        compute_Alfvenicity_params!
        @subset(.!isnan.(:v_l_ratio))
    end

    spec = data(tdf) *
           mapping([𝒎.l_log, 𝒎.j_log, 𝒎.l_norm_log, 𝒎.j_norm_log, 𝒎.v_l_ratio, 𝒎.bn], layout=AoG.dims(1) => renamer(ones(String, 6))) *
           mapping(color=:id) *
           AoG.density(datalimits=datalimits_f)

    draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
    easy_save("$fname-$enc-$𝐧"; formats, force=true)
end
```

>>>>

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using Discontinuity: compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using SPEDAS
using DimensionalData
using DataFrames, DataFramesMeta
using SpacePhysicsMakie, GLMakie
using SPEDAS: setmeta, setmeta!
using Beforerr: _theme_legend, easy_save
using PartialFunctions

@@

𝐧 = :mva
𝒎 = var_mapping(; 𝐧)

@@

```{julia}
f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[5, :]
fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
@info "v_l_ratio" psp_event.V_l_ratio psp_event.V_l_ratio_max
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
f
```

@@

### Alfvén ratio over time

@@

```{julia}
using AlgebraOfGraphics
using Discontinuity: compute_params!, compute_Alfvenicity_params!
using Beforerr
using Beforerr: add_labels!
# using CairoMakie
using StatsBase
# CairoMakie.activate!()

set_AoG_theme!()
formats = (:pdf,)

@@

# df, configs = workload()
compute_params!(df)

@@

@@
